title: "Lab3"
output: html_notebook
---
install packages
```{r}
install.packages("ggplot2")
library(ggplot2)
install.packages("dplyr")
library(dplyr)
install.packages("imager")
library(imager)
install.packages("tidyr")
library(tidyr)
install.packages("reshape2")
library(reshape2)
```

```{r}
im <- load.image("./lab3test.png")
bdf <- as.data.frame(im)
head(bdf,3)
plot(im)
```
Get info on image
```{r}
dim(im)
```
create a histogram for each color channels rgb value frequency

```{r}
R(im) %>% hist(main="Red Band values Frequency in Test Image");G(im) %>% hist(main="Green Band values Frequency in Test Image");B(im) %>% hist(main="Blue Band values Frequency in Test Image")
```
Create a data frame to store pic in and create header for df and plot it
```{r}
picdataframe <- as.data.frame(im)
head(picdataframe,3)
```
 use picture data frame with gg plot to create 3 histograms for each channels pixel freq
```{r}
picdataframe <- plyr::mutate(picdataframe,channel=factor(cc,labels=c('Red','Green','Blue')))
ggplot(picdataframe,aes(value,col=channel))+geom_histogram(bins=45)+facet_wrap(~ channel)
```
Plot equlaized image
```{r}
hist.eq <- function(im) as.cimg(ecdf(im)(im),dim=dim(im))
split <- imsplit(im,"c")
split
split.eq <- llply(split,hist.eq)
imappend(split.eq,"c") %>% plot(main="3 channel Hist Equalization using Empricial Cumulative Distribution Function")
```

Perform Image Gradient Magnitude analysis
```{r}
im.g <- grayscale(im)
imgradient(im.g,"xy") %>% enorm %>% plot(main="Gradient magnitude")
im.g
```
Calculating Hessian values using Image gradient
```{r}
imhessian(im.g)
```
Determine Determinat of Hessian matrix
```{r}
Hdet <- with(imhessian(im),(xx*yy - xy^2))
plot(Hdet,main="Determinant of Hessian")
```
Map the top 1% of Determinant values (high change areas)
```{r}
threshold(Hdet,"99%") %>% plot(main="Determinant: 1% highest values")
```
For programs sake label regions
```{r}
lab <- threshold(Hdet,"99%") %>% label
plot(lab,main="Labeled regions")
```
Convert to a df, plot df

```{r}
df <- as.data.frame(lab) %>% subset(value>0)
head(df,3)
```

 Calculate center
 
```{r}
centers <- ddply(df,.(value),summarise,mx=mean(x),my=mean(y))
```
```{r}
plot(im)
with(centers,points(mx,my,col="red"))
```
Blob detection using multi scalular aproach
  1- blur images to reduce noise
  2- Determine Hessian values at different zoome levels(scale)
  3- Plot deteriment values for each scale using gg plot
```{r}
hessdet <- function(im,scale=1) isoblur(im,scale) %>% imhessian %$% { scale^2*(xx*yy - xy^2) }
dat <- ldply(c(5,3,4),function(scale) hessdet(im,scale) %>% as.data.frame %>% mutate(scale=scale))
p <- ggplot(dat,aes(x,y))+geom_raster(aes(fill=value))+facet_wrap(~ scale)
p+scale_x_continuous(expand=c(0,0))+scale_y_continuous(expand=c(0,0),trans=scales::reverse_trans())
```
```{r}
scales <- seq(2,20,l=10)
d.max <- llply(scales,function(scale) hessdet(im,scale)) %>% parmax
plot(d.max,main="Point-wise maximum across scales")
```
Calculate the max across the multiple scales
plot results of max hessian value colored by scale
```{r}
i.max <- llply(scales,function(scale) hessdet(im,scale)) %>% which.parmax
plot(i.max,main="Maximum Hessian Value across scales")
```
Use ggplot to plot the grey scale imagery plus the mean centers of highest .1% of hessian values  with triangles over top of them (size of the triangle indicates how many times the center was picked up in the multi scale analysis)

```{r}
labs <- d.max %>% threshold("99.9%") %>% label %>% as.data.frame
labs <- mutate(labs,index=as.data.frame(i.max)$value)
regs <- dplyr::group_by(labs,value) %>% dplyr::summarise(mx=mean(x),my=mean(y),scale.index=mean(index))
p <- ggplot(as.data.frame(im),aes(x,y))+geom_raster(aes(fill=value))+geom_point(data=regs,aes(mx,my,size=scale.index),pch=2,col="red")
p+scale_fill_gradient(low="black",high="white")+scale_x_continuous(expand=c(0,0))+scale_y_continuous(expand=c(0,0),trans=scales::reverse_trans())
```

```{r}
imrow(R(im),10) %>% plot(main="Red channel along 10th row",type="l")
```


easier than scrolling up
```{r}
plot(im)
```

```{r}
im
d <- as.data.frame(im)
m <- sample_n(d,1e4) %>% lm(value ~ x*y,data=.) 
im.c <- im-predict(m,d)
out <- threshold(im.c)
plot(out)
```
```{r}
imblur<-grayscale(isoblur(im,5, gaussian =TRUE))
plot(imblur)
plot(im)

```

```{r}
threshold(imblur) %>% plot
```
Playing with methods of plotting multiple spectral plots
first attempt

```{r}

both<-("./plots.csv")
bothDf<-read.csv(both)
ggplot(data = bothDf, aes(x=WaveLength, y=Rrs_sim)) + geom_line(aes(y=Rrs_sim, colour=Rrs_sim)) +geom_line(aes(y=Rrs_lid, colour=Rrs_lid))
```

2nd attempt with data "melted" into long form
```{r}

melted.both <- melt(bothDf, id="WaveLength")  # convert to long format
melted.both

ggplot(data=test_data_long,
       aes(x=WaveLength, y=value, colour=variable)) +
       geom_line()
```

