title: "Lab3"
output: html_notebook
---
install packages
```{r}
install.packages("ggplot2")
library(ggplot2)
install.packages("dplyr")
library(dplyr)
install.packages("imager")
library(imager)
```

```{r}
im <- load.image("D://Users//drewk1992//Documents//UGA//Thesis//Pictures//lab3Test.png")
bdf <- as.data.frame(im)
head(bdf,3)
plot(im)
```
Get info on image
```{r}
dim(im)
```
create a histogram for each color channels rgb value frequency

```{r}
R(im) %>% hist(main="Red channel values in mine picture");G(im) %>% hist(main="Red channel values in mine picture");B(im) %>% hist(main="Red channel values in mine picture")
```
Create a data frame to store pic in and create header for df and plot it
```{r}
picdataframe <- as.data.frame(im)
head(picdataframe,3)
```
 use picture data frame with gg plot to create 3 histograms for each channels pixel freq
```{r}
picdataframe <- plyr::mutate(picdataframe,channel=factor(cc,labels=c('R','G','B')))
ggplot(picdataframe,aes(value,col=channel))+geom_histogram(bins=30)+facet_wrap(~ channel)
```
Plot equlaized image
```{r}
hist.eq <- function(im) as.cimg(ecdf(im)(im),dim=dim(im))
split <- imsplit(im,"c")
split
split.eq <- llply(split,hist.eq)
imappend(split.eq,"c") %>% plot(main="3 channel Hist Equalization")
```

Perform Image Gradient Magnitude analysis
…
```{r}
im.g <- grayscale(im)
imgradient(im.g,"xy") %>% enorm %>% plot(main="Gradient magnitude")
```
```{r}
imhessian(im.g)
```
```{r}
Hdet <- with(imhessian(im),(xx*yy - xy^2))
plot(Hdet,main="Determinant of Hessian")
```
```{r}
threshold(Hdet,"99%") %>% plot(main="Determinant: 1% highest values")
```

```{r}
lab <- threshold(Hdet,"99%") %>% label
plot(lab,main="Labelled regions")
```
```{r}
df <- as.data.frame(lab) %>% subset(value>0)
head(df,3)
```

 Calculate center
 
```{r}
centers <- ddply(df,.(value),summarise,mx=mean(x),my=mean(y))
```
```{r}
plot(im)
with(centers,points(mx,my,col="red"))
```
Blob detection using multi scalular aproach
```{r}
hessdet <- function(im,scale=1) isoblur(im,scale) %>% imhessian %$% { scale^2*(xx*yy - xy^2) }
dat <- ldply(c(2,3,4),function(scale) hessdet(im,scale) %>% as.data.frame %>% mutate(scale=scale))
p <- ggplot(dat,aes(x,y))+geom_raster(aes(fill=value))+facet_wrap(~ scale)
p+scale_x_continuous(expand=c(0,0))+scale_y_continuous(expand=c(0,0),trans=scales::reverse_trans())
```
```{r}
scales <- seq(2,20,l=10)

d.max <- llply(scales,function(scale) hessdet(im,scale)) %>% parmax
plot(d.max,main="Point-wise maximum across scales")
```
Calculate the max across the multiple scales
```{r}
i.max <- llply(scales,function(scale) hessdet(im,scale)) %>% which.parmax
plot(i.max,main="Index of the point-wise maximum \n across scales")
```
Use ggplot to plot the grey scale imagery plus the mean centers with triangles over top of them (size of the triangle indicates how many times the center was picked up in the multi scale analysis)

```{r}
labs <- d.max %>% threshold("99.9%") %>% label %>% as.data.frame
labs <- mutate(labs,index=as.data.frame(i.max)$value)
regs <- dplyr::group_by(labs,value) %>% dplyr::summarise(mx=mean(x),my=mean(y),scale.index=mean(index))
p <- ggplot(as.data.frame(im),aes(x,y))+geom_raster(aes(fill=value))+geom_point(data=regs,aes(mx,my,size=scale.index),pch=2,col="red")
p+scale_fill_gradient(low="black",high="white")+scale_x_continuous(expand=c(0,0))+scale_y_continuous(expand=c(0,0),trans=scales::reverse_trans())
```


Now to work on image gradient

load image as a image gradient image and convert to dataframe
```{r}
grad <- imgradient(im,"xy")
names(grad) <- c("dx","dy")
dfgr <- as.data.frame(grad)
head(dfgr)
```

Recomended for ggplot defaults
```{r}
install.packages("cowplot")
library(cowplot)
```

